### 2022-02-02 R Markdown Template.Rmd
Update R Markdown Template.Rmd

---
title: ""
author: "Tim Vigers & Laura Pyle"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD//PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
knitr::opts_knit$set(root.dir = home_dir)
```

>>>>

---
title: ""
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
knitr::opts_knit$set(root.dir = home_dir)
```
